Title of the document here

### 2015-01-26 rmtw/assignment_1/assignment_1.tex
Made a teebel

The importance of code readability may be overlooked, since it does not directly affect runtime performance. Aggarwal et al., however claim that code's readability impacts it's maintainability \cite{aggarwal2002integrated}. This claim is also supported by \cite{elshoff1982improving} et al. who also introduce examples of certain coding practices that are more readable and maintainable than others \cite{elshoff1982improving}.
\newline

@@

Both industry and academia face the problem of maintainability. As stated previously, many times the readability of code affects the codes maintainability. This study could help some in industry to pick languages for certain tasks for maintainability reasons alone. Further studies could be conducted by to determine if there is a correlation between the popularity of projects and the readability of their languages. Furthermore, academia would be interested in which languages are more popular and useful for learning. By further investigating the design of the programming languages themselves, future languages which are developed could build upon the success of those which came before them.
\newline
The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages. With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
\newline

@@

%------------------------------------------------------------------------- 
\SubSection{Research Question}
*State a clear and concise main  research  question  that  will  be  investigated
*State another one or  two sub research  questions related to  the main  RQ.

What are the measurable differences in readability between programming languages.

How do the measurable differences between languages correlate to their use in academia for teaching?

How do the measurable differences between languages correlate to the popularity of the language 
%------------------------------------------------------------------------- 
\SubSection{Methodology}

>>>>

The importance of code readability may be overlooked, since it does not directly affect runtime performance. Aggarwal et al., however claim that code's readability impacts it's maintainability \cite{aggarwal2002integrated}. This claim is also supported by \cite{elshoff1982improving} et al. who also introduce examples of certain coding practices that are more readable and maintainable than others \cite{elshoff1982improving}.

@@

Both industry and academia face the problem of maintainability. As stated previously, many times the readability of code affects the codes maintainability. This study could help some in industry to pick languages for certain tasks for maintainability reasons alone. Further studies could be conducted by to determine if there is a correlation between the popularity of projects and the readability of their languages. Furthermore, academia would be interested in which languages are more popular and useful for learning. By further investigating the design of the programming languages themselves, future languages which are developed could build upon the success of those which came before them.
\newline

The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages. With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
\newline

@@

%------------------------------------------------------------------------- 
\SubSection{Research Question}
This study has been designed with one main research question in mind:
\begin{itemize}
\item \textit{RQ1:} What are the measurable differences in readability between programming languages?
\end{itemize}

The results of RQ1 will then be used to answer the following two sub research questions. 
\begin{itemize}
\item \textit{SRQ1}: How do the measurable differences between languages correlate to their use in academia for teaching?
\item \textit{SRQ2}: How do the measurable differences between languages correlate to the popularity of the language?
\end{itemize}

\begin{tabular}{| l | r | c |}
	\hline
	\textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
	Occupation & RQ1, SQ1 & \\ \hline
	Experience & RQ1, SQ1 & \\ \hline
	Preferred Language & RQ1, SQ2 & \\ \hline
	Least Preferred Language & RQ1, SQ2& \\  \hline
	Working Language & RQ1, SQ2 & \\ 
	\hline
	\end{tabular}
%------------------------------------------------------------------------- 
\Section{Methodology}
